SDR enhancement by clouds

### 2024-03-15 article/article.tex
Commit 2024-03-15 15:12

\title{SDR enhancement by clouds}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A Short Subtitle}
\author{Athanasios N. Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
\date{2024-03-12}

\begin{document}
\maketitle
\begin{abstract}
This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo rutrum at. Sed at tempus elit.
\end{abstract}

{
\setcounter{tocdepth}{4}
\tableofcontents
}
CE: cloud enhancement cases one minute

@@

@@

CE and ECE usefulness

@@

\ldots.identification methods from bib\ldots.

@@

\ldots..constrains of the site\ldots..

@@

\begin{itemize}
\tightlist
\item
  measured data
\item
  available data

@@

The recording of the signal is the one minute average.
Thus we will refer to this time scale as a cloud enhancement event (CE).
Due to the instruments response time\ldots..

\hypertarget{data-quality-control}{%
\subsection{Data quality control}\label{data-quality-control}}

.. todo \ldots{}

\hypertarget{data-selection}{%
\subsection{Data selection}\label{data-selection}}

To preserve an unbiased representation of the data we applied a constrain similar the one used by Castillejo-Cuberos and Escobar (2020). Where, for each valid hour of day, there must exist at list 45 minutes of valid measurements, including night time near sunrise and sunset. Days with less than 5 valid hours are rejected completely. Furthermore, due to a systematic obstruction of the horizon and the significant measurement uncertainty on large SZAs, we excluded all data with \(SZA > 78^\circ\).

@@

In order to set a threshold for the CE we had to create an approximation of ``clear sky'' radiation for the whole period.
For this reason, we decided to use the Libradtran model (Emde et al. 2016), with monthly climatological data for AOD and water column from AERONET (Giles et al. 2019; Buis et al. 1998). Our site is part of AERONET monitoring network and operates a Cimel photometer since 2003.
We also use the Sun's total solar irradiance from NOAA (Coddington et al. 2005) and Earth - Sun distance calculated by Astropy (Astropy Collaboration et al. 2022).
We have simulated the solar radiation spectrum of Kurucz (1994) in the range \(280\) to \(2500\,\text{nm}\), on \(0.2^\circ\) SZA's step.
With combinations of AOD at \(500\,\text{nm}\) (\(t_{500\text{nm}}\)) and additional offsets of \(\pm1\) and \(\pm2\sigma\), water column (\(w_h\)) with offsets of \(\pm1\) and \(\pm2\sigma\), and for two atmospheric profiles ``AFGL atmospheric constituent profile, midlatitude summer'' (afglms) and ``AFGL atmospheric constituent profile, midlatitude winter'' (afglmw) (Anderson et al. 1986).

@@

For each GHI measurement in our data we calculated a reference clear sky value, by adjusting the integral of the Kurudz spectrum to the interpolated TSI from NOAA. We applied the effect of Sun - Earth distance, and calculated it's value to the horizontal plane by using the cosine of the corresponding interpolated SZA.
For each period of the year, we used the appropriate atmospheric profile (afglms or afglmw).
Thus, we can directly compare each measured one minute value of GHI, with the expected clear sky radiation.

@@

To select the exact values of the threshold used (Equation \ref{eq:CE4}), we implemented manual inspection of the CE indemnification, on specially selected days from the whole dataset.
We used seven sets of random selected days, with characteristics relevant to the efficiency of the threshold.

six criteria in order to evaluate random multiples of 25 days with some characteristics

\begin{itemize}
\tightlist
\item
  20 days with the largest over irradiance CE events
\item
  30 days with largest total over irradiance
\item
  20 days without clouds (CSid) Natsis, Bais, and Meleti (2023)
\item
  any day without clouds and EC events
\item
  20 days with at least 60\% of day length without clouds and some EC events
\item
  30 random days
\item
  some manual selected days that were included during the manual inspection
\end{itemize}

For some of this edge cases we further use images from a sky-cam, in order to evaluate our selection of the thresholds.

Thresholds by inspecting a selection of days with some specs\ldots\ldots{}

Reasoning for the selection\ldots\ldots\ldots..

@@

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/daily-12}

\caption{Trend of the daily excess energy due to CE}(\#fig:unnamed-chunk-1)
\end{figure}

@@

\caption{Treds of the mean over irradiance per CE}(\#fig:unnamed-chunk-2)
\end{figure}

@@

\caption{Trend of number of CE cases}(\#fig:unnamed-chunk-3)
\end{figure}

@@

\caption{Trend of the yearly excess energy due to CE over irradiance}(\#fig:unnamed-chunk-4)
\end{figure}

@@

\caption{Distribution of the number of CE cases}(\#fig:unnamed-chunk-5)
\end{figure}

@@

\caption{Distribution of CE above reference}(\#fig:unnamed-chunk-6)
\end{figure}

@@

\caption{Distribution of CE groups}(\#fig:unnamed-chunk-7)
\end{figure}

@@

\caption{Relation of mean over irradiance and CE group duration}(\#fig:unnamed-chunk-8)
\end{figure}

@@

\caption{Relation of maximun over irradiance and CE group duration}(\#fig:unnamed-chunk-9)
\end{figure}

@@

\caption{Distribution of the number of ECE cases}(\#fig:unnamed-chunk-10)
\end{figure}

@@

\caption{Distribution of ECE above 'clear sky' reference}(\#fig:unnamed-chunk-11)
\end{figure}

@@

\caption{Distribution of ECE Irradiance above 'TSI'}(\#fig:unnamed-chunk-12)
\end{figure}

@@

@@

\caption{Distribution of }(\#fig:unnamed-chunk-14)
\end{figure}

@@

>>>>

\title{SDR enhancement by clouds}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A Short Subtitle}
\author{Athanasios N. Natsis\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:abais@auth.gr}{\nolinkurl{abais@auth.gr}}}} \and Charikleia Meleti\footnote{Laboratory of Atmospheric Physics \emph{\href{mailto:meleti@auth.gr}{\nolinkurl{meleti@auth.gr}}}}}
\date{2024-03-15}

\begin{document}
\maketitle

{
\setcounter{tocdepth}{4}
\tableofcontents
}
\hypertarget{abstract}{%
\section*{Abstract}\label{abstract}}
\addcontentsline{toc}{section}{Abstract}

\begin{itemize}
\tightlist
\item
  Phenomenon
\item
  Effects
\item
  bibliography
\item
  our approach
\item
  our results
\end{itemize}

CE: cloud enhancement cases one minute

@@

\(\text{GHI}_\text{i}\): measured one minute global horizontal irradiance

\(\text{GHI}_\text{mCSi}\): modeled clear sky one minute global horizontal irradiance

@@

CE and ECE usefulness
importance
problems

reported trends

CE mechanism

In this study, we define as cloud enhancement events (CE) the cases when the measured
global horizontal irradiance (GHI) at ground level, exceeds the expected value under
clear-sky conditions.
Similar, we define the extreme cloud enhancement events (ECE), the cases when GHI,
exceeds the Total Solar Irradiance on horizontal plane at ground level.
Although the duration of these bursts varies form instantaneous to several minutes,
here we are constrained by the recorded data, to one-minute steps.

@@

Identification methods from bib

@@

Constrains of the site

@@

\hypertarget{ghi-data}{%
\subsection{GHI data}\label{ghi-data}}

Our monitoring site is operating in the Laboratory of Atmospheric Physics of the
Aristotle University of Thessaloniki (\(40^\circ\,38'\,\)N,
\(22^\circ\,57'\,\)E, \(80\,\)m~a.s.l.).
In this study we present data from the period
13~April 1993 to
31~December 2023.

The GHI data were measured with a Kipp~\& Zonen CM-21 pyranometer.
During the study period, the pyranometer was independently calibrated three times at
the Meteorologisches Observatorium Lindenberg, DWD, verifying that the stability of
the instrument's sensitivity was better than \(0.7\%\) relative to the initial
calibration by the manufacturer.

For the acquisition of radiometric data, the signal of the pyranometer was sampled
at a rate of \(1\,\text{Hz}\).
The mean and the standard deviation of these samples were calculated and recorded
every minute.
The measurements were corrected for the zero offset (``dark signal'' in volts), which
was calculated by averaging all measurements recorded for a period of \(3\,\text{h}\),
before (morning) or after (evening) the Sun reaches an elevation angle of \(-10^\circ\).
The signal was converted to irradiance using a ramped value of the instrument's
sensitivity between subsequent calibrations.

To further improve the quality of the irradiance data, a manual screening was
performed to remove inconsistent and erroneous recordings that can occur
stochastically or systematically during the continuous operation of the instruments.
The manual screening was aided by a radiation data quality assurance procedure,
adjusted for the site, which was based on the methods of Long and Shi~(Long and Shi 2006, 2008).
Thus, problematic recordings have been excluded from further processing.
Although it is impossible to detect all false data, the large number of available
data, and the aggregation scheme we used, ensures the quality of the radiation
measurements used in this study.

To preserve an unbiased representation of the data we applied a constrain similar
the one used by Castillejo-Cuberos and Escobar (2020). Where, for each valid hour of day, there
must exist at list 45 minutes of valid measurements, including night time near
sunrise and sunset. Days with less than 5 valid hours are rejected completely.
Furthermore, due to the significant measurement uncertainty when the Sun is near the
horizon, and to some systematic obstructions by nearby buildings, we have excluded
all measurements with solar zenith angle (SZA) greater than \(78^\circ\).

In this study, we evaluated the effects of the clouds on th

\begin{itemize}
\tightlist
\item
  available data

@@

The recording of the signal is the one minute average.
Thus we will refer to this time scale as a cloud enhancement event (CE).

@@

In order to identify CE cases, we need an approximation of the expected clear sky GHI
for the whole period of the study, with a temporal resolution of one minute. Because
of the lack of exact data about atmospheric factors, responsible for the attenuation
of the solar radiation in the atmosphere, we can not recreate a minute by minute
representation of the reference radiation. Thus, we used some climatological data
with a radiation transfer model.

We decided to use the Libradtran (Emde et al. 2016) radiation transfer model, to modeled
the clear sky equivalent of GHI, with monthly climatological data of AOD and water
column from the Aerosol Robotic Network (AERONET) (Giles et al. 2019; Buis et al. 1998). Our site
participates in AERONET, where we operate a Cimel photometer, colocated to
the CM-21 pyranometer, since 2003

For the production of \ldots..

We also used the Sun's total solar irradiance from NOAA (Coddington et al. 2005) and the
Earth - Sun distance calculated by Astropy (Astropy Collaboration et al. 2022). We simulated
the clear sky radiation, using the solar radiation spectrum of Kurucz (1994) in the
range \(280\) to \(2500\,\text{nm}\), with a SZA step of \(0.2^\circ\). For the
atmospheric characteristics, we used combinations of AOD at \(500\,\text{nm}\)
(\(t_{500\text{nm}}\)) and additional offsets of \(\pm1\) and \(\pm2\sigma\), water column
(\(w_h\)) with offsets of \(\pm1\) and \(\pm2\sigma\), and applied it to two atmospheric
profiles ``AFGL atmospheric constituent profile, midlatitude summer'' (afglms) and
``AFGL atmospheric constituent profile, midlatitude winter'' (afglmw) (Anderson et al. 1986).
Thus, we were able to emulate different atmospheric condition and level of
atmospheric clearness for the climatological conditions of the site.

Furthermore, to account for the Sun's variability in our one-minute GHI measurements,
we adjusted the model's input spectrum integral to the one of the the TSI provided by
NOAA. Finally, we adjusted for the effect of the Sun - Earth distance, and
calculated the clear sky irradiance value at the horizontal plane by using the cosine
of the corresponding interpolated SZA. For each period of the year, we used the
appropriate atmospheric profile (afglms or afglmw). Thus, the modelled GHI\_modeld we
can directly compare each measured one minute value of GHI, with the expected clear
sky radiation.

\begin{itemize}
\tightlist
\item
  rte\_solver disort
\item
  geometry pseudospherical
\item
  mol\_abs LOWTRAN
\end{itemize}

Of course, have to choose which atmospheric conditions qualify as a good clear sky analogous radiation.

@@

Which is an expected result as these values represent an typical atmosphere in Thessaloniki with low load of aerosols and humidity, which are the main factor that attenuate the GHI, excluding clouds.

@@

The use of the actual modeled values of clear sky GHI can not provide us with a
robust method to distinguish the CE cases, due to the limited accuracy of the input
data. Our main focus was to positively identify over irradiance events from CEs,
thus we used a relative factor, to create an upper envelope of the clear sky
irradiance, above which, any GHI value can safely attributed to CE.

To select the exact values of the thresholds (Equation \ref{eq:CE4}), we implemented
manual inspection of the CE identification, on specially selected days from the whole
dataset. We used seven sets of selected days, with characteristics relevant to the
efficiency of the identification threshold. These sets were random groups of about
20 to 30 days with the following characteristics:
(a) the largest over irradiance CE events,
(b) the largest daily total over irradiance,
(c) without clouds (by implementing a clear sky identification algorithm as discussed in Natsis, Bais, and Meleti (2023)),
(d) without clouds and without EC events,
(e) with at least \(60\%\) of the day length without clouds and some EC events,
(h) random days and
(i) some manual selected days that were included during the manual inspection.

Where it was needed, for some of edge cases, we also used images from a sky-cam,
along with the manual inspection.

Reasoning for the final selection\ldots\ldots\ldots..

@@

Our dataset, after the data selection processing, consists of
6144534 records of GHI, of which
\(1.799\,\%\) are CE and
\(0.036\,\%\) are ECE events.
The highest GHI recorder was
\(1416.6\,W/m^2\)
on 24~May 2007.
The absolute stronger CE event had an over irradiance of
\(341.79\,W/m^2\) on
15~May 2014.
The relative stronger CE event was
\(54\,\%\) above the
clear sky threshold, on
28~October 2016.

\hypertarget{trends}{%
\subsection{Trends}\label{trends}}

We have computed the daily trend of the mean over irradiance of CE (Figure~\ref{fig:CEmeanDaily}), using

\ldots. cite arima lag \ldots.

{\centering \includegraphics[width=0.7\linewidth]{../images/P_daily_trend-1}

\caption{Daily mean values and trend of the CE over irradiance.}(\#fig:CEmeanDaily)
\end{figure}

We observe an increase of
\(0.216\pm 0.041\,W/m^2\)
on the mean over irradiance.

By computing the mean daily over irradiance for all the CE case, we were able to dirive a trend on the mean CE intensity of \ldots..

Figures~\ref{fig:CEmeanDaily}

@@

@@

\caption{Treds of the mean over irradiance per CE}(\#fig:unnamed-chunk-1)
\end{figure}

@@

\caption{Trend of number of CE cases}(\#fig:unnamed-chunk-2)
\end{figure}

@@

\caption{Trend of the yearly excess energy due to CE over irradiance}(\#fig:unnamed-chunk-3)
\end{figure}

@@

\caption{Distribution of the number of CE cases}(\#fig:unnamed-chunk-4)
\end{figure}

@@

\caption{Distribution of CE above reference}(\#fig:unnamed-chunk-5)
\end{figure}

@@

\caption{Distribution of CE groups}(\#fig:unnamed-chunk-6)
\end{figure}

@@

\caption{Relation of mean over irradiance and CE group duration}(\#fig:unnamed-chunk-7)
\end{figure}

@@

\caption{Relation of maximun over irradiance and CE group duration}(\#fig:unnamed-chunk-8)
\end{figure}

@@

\caption{Distribution of the number of ECE cases}(\#fig:unnamed-chunk-9)
\end{figure}

@@

\caption{Distribution of ECE above 'clear sky' reference}(\#fig:unnamed-chunk-10)
\end{figure}

@@

\caption{Distribution of ECE Irradiance above 'TSI'}(\#fig:unnamed-chunk-11)
\end{figure}

@@

\caption{Distribution of }(\#fig:unnamed-chunk-12)
\end{figure}

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-Long2006}{}}%
Long, Charles N., and Y. Shi. 2006. {``The QCRad Value Added Product: Surface Radiation Measurement Quality Control Testing, Including Climatology Configurable Limits.''} DOE/SC-ARM/TR-074. Office of Science, Office of Biological; Environmental Research, U.S. Department of Energy.

\leavevmode\vadjust pre{\hypertarget{ref-Long2008a}{}}%
---------. 2008. {``An Automated Quality Assessment and Control Algorithm for Surface Radiation Measurements.''} \emph{The Open Atmospheric Science Journal}, 23--37.
